# Conclusion


<!--chapter:end:Conclusion.Rmd-->

# EDA

## Data Acquisition

To download the differents speaches we scrap the speaches on 2 differents websites.
The speaches from Macron come from the website of the Embassy of France in Washington DC (USA) and regarding Boris Johnson speaches, it comes from the official website of the governement of the United-Kingdom.

### Emmanuel Macron 

We choose the 3 first speaches from Macron about the corona virus dating from the:
  - 12 march (text1)
  - 16 march (text2)
  - 13 april (text3)

```{r include=FALSE}
packages <- c(
  "here", "readr",# for the project's organization
  "tidyverse", "lubridate", # for wrangling
  "modelr", "broom",
  "dplyr",# for modeling
  "ggrepel", "gghighlight", "patchwork", "maps", # for plotting
  "knitr", "kableExtra", "bookdown", "rmarkdown", # for the report
  "randomForest","janitor","caret","pdftools","rvest","wordcloud2","tidytext","tokenizers","quanteda","sentimentr",
  "stringr","lexicon","RColorBrewer","tm","printr","ggplot2","quanteda.textmodels","topicmodels","text2vec", "DT")

purrr::walk(packages, library, character.only = TRUE)

# automatically create a bib database for R packages
write_bib(.packages(), here::here("packages.bib"))

# Data Acquisition Macron 

macron12march <- read_html("https://franceintheus.org/spip.php?article9654") %>%
  html_nodes("div.texte") %>%
  html_text()
macron12march <- str_replace_all(macron12march,"[\r\n\t]", "")
macron12march <- substr(macron12march, 178, 20197)

macron16march <- read_html("https://franceintheus.org/spip.php?article9659#1") %>%
  html_nodes("div.texte") %>%
  html_text()
macron16march <- macron16march <- str_replace_all(macron16march,"[\r\n\t]", "")
macron16march <- substr(macron16march, 131, 15719)

macron13april <- read_html("https://franceintheus.org/spip.php?article9710") %>%
  html_nodes("div.texte") %>%
  html_text() 
macron13april <- macron13april <- str_replace_all(macron13april,"[\r\n\t]", "")
macron13april <- substr(macron13april, 117, 20000)


macron <- corpus(c(macron12march,macron16march,macron13april))
```

```{r }
summary(macron)
```
The first speaches from Macron was quite long , 162 sentences and the two next were shorter: 107 sentences. Each speech consists approximatly of an average of 3200 words.

### Boris Johnson

We choose the 7 first speaches from president Johnson about the corona virus dating from the:
  - 09 march (text1)
  - 12 march (text2)
  - 16 march (text3)
  - 18 march (text5)
  - 19 march (text6)
  - 20 march (text7)
  - 22 march (text8)

```{r include=FALSE}

# Data Acquisition Boris

boris16mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-16-march-2020") %>%
                html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>% 
                html_text()

boris12mars<- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-12-march-2020") %>%   
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris18mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-18-march-2020") %>%   
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris9mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-9-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris19mars<- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-19-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris20mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-20-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()


boris22mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-22-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()


boris<-corpus(c(boris9mars,boris12mars,boris16mars,boris18mars,boris19mars,boris20mars,boris22mars))
```

```{r }
summary(boris) ###number of tokens and token types
```
Johnson made more speeches but shorter. His first speech was 577 words, then the following ones ranged from 729 to 1175 words.

## Tokenisation, Lemmatization & Cleaning

### Emmanuel Macron


```{r}

## Tokenization
corpus_macron <- corpus(macron)
corpus_macron <- tokens(corpus_macron, remove_numbers = TRUE, remove_punct = TRUE, remove_symbols = TRUE, remove_separators = TRUE)

## Lemmatization
corpus_macron <- tokens_replace(corpus_macron, pattern=hash_lemmas$token, replacement = hash_lemmas$lemma)

## Cleaning
corpus_macron=corpus_macron %>% 
  tokens_tolower() %>% 
  tokens_remove(stopwords("english")) 

corpus_macron

```

### Boris Johnson

```{r}

## Tokenization
corpus_boris <- corpus(boris)
corpus_boris <- tokens(corpus_boris, remove_numbers = TRUE, remove_punct = TRUE, remove_symbols = TRUE, remove_separators = TRUE)

## Lemmatization
corpus_boris <- tokens_replace(corpus_boris, pattern=hash_lemmas$token, replacement = hash_lemmas$lemma)

## Cleaning
corpus_boris = corpus_boris %>% 
  tokens_tolower() %>% 
  tokens_remove(stopwords("english")) 

corpus_boris

```

## Document-Term Matrix DTM

Now let's compute the word frequencies (TF) by documents. First, the tokens are grouped by the indicator Document, which allows to count the words by documents. The the object is ungrouped.


These frqeuencies are represented with barplots. We only keep the 15 most frequent words for redability purpose and create barplots using ggplot and geom_col. The facetwrap function split the barplots per Document.

We see that the list of 15 most frequent term are due to doc 2 ,4 and 3. 

Now we want to know which are  the most frequent term for each document

### Emmanuel Macron

```{r  include=TRUE, warning=FALSE}
## Document-Term Matrix DTM
corpus_macron.dfm <- dfm(corpus_macron)

macron_dtm <- VectorSource(corpus_macron) %>% VCorpus() %>%  DocumentTermMatrix(control=list(removePunctuation=TRUE, removeNumbers=TRUE, stopwords=TRUE))
macron_tidy <- tidy(macron_dtm)

datatable(macron_tidy, class = "cell-border stripe")

#top 15 
macron_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`)) %>%
  top_n(15)  %>%
  ggplot(aes(x=count, y=term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Macron's speeches") +
  xlab("Frequency") + ylab("Word") +
  geom_bar(stat = "identity") +
  scale_y_reordered() 

#top 15 par texte 
macron_tidy %>%
  group_by(document) %>%
  top_n(15) %>%
  ungroup() %>%
  mutate(document = factor(as.numeric(document), levels = 1:17)) %>%
  ggplot(aes(reorder_within(term, count, document), count, fill =term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Macron's speech") +
  xlab("Word") + ylab("Frequency") +
  geom_bar(stat = "identity") +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~ document, scales = "free")

#top 16 mots plus utilisés par texte
macron_count  = macron_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`))

macron_index = top_n(macron_count, 15)

macron_tidy %>% filter(term %in% macron_index$term) %>%
  ggplot(aes(x=term, y = count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```

### Boris Johnson

```{r}

## Document-Term Matrix DTM
corpus_boris.dfm <- dfm(corpus_boris)

boris_dtm <- VectorSource(corpus_boris) %>% VCorpus() %>%  DocumentTermMatrix(control=list(removePunctuation=TRUE, removeNumbers=TRUE, stopwords=TRUE))
boris_tidy <- tidy(boris_dtm)

datatable(boris_tidy, class = "cell-border stripe")


#top 15
boris_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`)) %>%
  top_n(15)  %>%
  ggplot(aes(x=count, y=term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Boris Johnson's speeches") +
  xlab("Frequency") + ylab("Word") +
  geom_bar(stat = "identity") +
  scale_y_reordered() 

#top 15 par texte
boris_tidy %>%
  group_by(document) %>%
  top_n(15) %>%
  ungroup() %>%
  mutate(document = factor(as.numeric(document), levels = 1:17)) %>%
  ggplot(aes(reorder_within(term, count, document), count, fill =term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Boris Johnson's speeches") +
  xlab("Word") + ylab("Frequency") +
  geom_bar(stat = "identity") +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~ document, scales = "free")

#top 16 mots plus utilisés par texte
boris_count  = boris_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`))

boris_index = top_n(boris_count, 15)

boris_tidy %>% filter(term %in% boris_index$term) %>%
  ggplot(aes(x=term, y = count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```
## TF-IDF

Now we repeat the same analysis using the TF-IDF.

### Emmanuel Macron 
```{r  include=TRUE, warning=FALSE}
## TFIDF no point when just on document, maybe add when combining texts
corpus_macron.tfidf <- dfm_tfidf(corpus_macron.dfm)

#tfidf
macron_index_tfidf = tidy(corpus_macron.tfidf) %>% group_by(document) %>% top_n(1)

tidy(corpus_macron.tfidf) %>% filter(term %in% macron_index_tfidf$term) %>%
  ggplot( aes(term, count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```
###Boris Johnson


```{r}
## TFIDF no point when just on document, maybe add when combining texts
corpus_boris.tfidf <- dfm_tfidf(corpus_boris.dfm)

#tfidf
boris_index_tfidf = tidy(corpus_boris.tfidf) %>% group_by(document) %>% top_n(1)

tidy(corpus_boris.tfidf) %>% filter(term %in% boris_index_tfidf$term) %>%
  ggplot( aes(term, count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```
## Cloud of Words

### Emmanuel Macron 
```{r}

## Cloud of Words
textplot_wordcloud(corpus_macron.dfm, color=brewer.pal(8, "Dark2"))
textplot_wordcloud(corpus_macron.tfidf, color=brewer.pal(8, "Dark2"))

```
### Boris Johnson

```{r}

## Cloud of Words
textplot_wordcloud(corpus_boris.dfm, color=brewer.pal(8, "Dark2"))
textplot_wordcloud(corpus_boris.tfidf, color=brewer.pal(8, "Dark2"))
```

## Lexical Divesity Token Type Ratio TTR

### Emmanuel Macron 
```{r}
## Lexical Divesity Token Type Ratio TTR
N.macron <- ntoken(corpus_macron)
V.macron <- ntype(corpus_macron)
TTR.macron <- V.macron/N.macron
TTR.macron ###the text is quite poor, as TTR is of 0.4

```
### Boris Johnson

```{r}
## Lexical Divesity Token Type Ratio TTR
N.boris <- ntoken(corpus_boris)
V.boris <- ntype(corpus_boris)
TTR.boris <- V.boris/N.boris
TTR.boris ###the text is quite rich, as TTR is of 0.6

```


##Zipf's Law

Now, we illustrate the Zipf's law on the discous of Boris Jonhson. The terms are ranked by their frequency (rank=1 for the most frequent), then plotted versus its rank. This is easily obtained using quanteda.

Now on the log scale this gives a linear relation

### Emmanuel Macron 
```{r}
corpus_macron_freq <- textstat_frequency(corpus_macron.dfm)
plot(log(frequency)~log(rank), data=corpus_macron_freq, pch=20)

ggplot(corpus_macron_freq,aes(x = rank, y = frequency, label=feature)) + geom_point(size=2, alpha =1) + theme_bw() + geom_text(aes(label=feature),hjust=0, vjust=0) + xlim(0,20)


```
### Boris Johnson

```{r}

corpus_boris_freq <- textstat_frequency(corpus_boris.dfm)
plot(log(frequency)~log(rank), data=corpus_boris_freq, pch=20)

ggplot(corpus_boris_freq,aes(x = rank, y = frequency, label=feature)) + geom_point(size=2, alpha =1) + theme_bw() + geom_text(aes(label=feature),hjust=0, vjust=0) + xlim(0,20)


```





## yule's index

### Emmanuel Macron 
```{r}
textstat_lexdiv(corpus_macron.dfm, measure = "I") %>% 
  ggplot(aes(x=reorder(document,I), y=I))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("Yule's index")
```
### Boris Johnson

```{r}
textstat_lexdiv(corpus_boris.dfm, measure = "I") %>% 
  ggplot(aes(x=reorder(document,I), y=I))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("Yule's index")
```


## MATTR

### Emmanuel Macron 
```{r}
textstat_lexdiv(corpus_macron, measure = "MATTR", MATTR_window = 10)  %>%
  ggplot(aes(x=reorder(document,MATTR), y=MATTR))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("MATTR")
```
### Boris Johnson

```{r}
textstat_lexdiv(corpus_boris, measure = "MATTR", MATTR_window = 10)  %>%
  ggplot(aes(x=reorder(document,MATTR), y=MATTR))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("MATTR")

```


<!--chapter:end:EDA.Rmd-->

# Introduction

## Overview and Motivation


## Data loadind

```{r data, echo=TRUE}
# Boris Johnson's speech of March 16th

boris16mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-16-march-2020")%>%            html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
  html_text()

macron <- read_html("https://franceintheus.org/spip.php?article9654") %>%
           html_nodes("div.texte") %>%
          html_text()

```


<!--chapter:end:Introduction.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`


<!--chapter:end:references.Rmd-->

# Sentiment Analasis

## Boris Johnson

We use the nrc dictionary. From the token list per document boris.tok, we join the corresponding qualifier in  nrc using inner.joint: 

```{r}
boris.sent<- boris.tok %>% inner_join(get_sentiments("nrc"))
head(boris.sent)

```

Then several summaries can be obtained. Below, using a table version and a long format

```{r}
table(boris.sent$Document,boris.sent$sentiment)

## Long format + barplots

boris.sent %>% 
  group_by(Document,sentiment) %>% 
  summarize(n=n())%>%
  ggplot(aes(x=sentiment,y=n,fill=sentiment)) +
  geom_bar(stat="identity",alpha=0.8) +
  facet_wrap(~ Document) +
  coord_flip()

```
to compare the document, we rescale them by their lenght

```{r}
boris.sent %>% 
  group_by(Document,sentiment) %>% 
  summarize(n=n())%>%
  mutate(freq=n/sum(n)) %>%
  ggplot(aes(x=sentiment,y=freq,fill=sentiment)) +
  geom_bar(stat="identity",alpha=0.8) +
  facet_wrap(~ Document) + 
  coord_flip()

```

### Value-based


Now we use the afinn dictionary. The main difference is that rach word receives a value rather than a qualifier. Then the average score per document is computed.

```{r}
head(get_sentiments("afinn"))
boris.sent <- boris.tok %>%
  inner_join(get_sentiments("afinn"))

aggregate(value~Document, data =boris.sent,FUN=mean) %>%
  ggplot(aes(x=Document,y=value)) +
  geom_bar(stat="identity") +
  coord_flip()


```

### With quanteda

The difference with tidytext is essentially in the manipulation of the objects. Note that this condition storngly the capactiy of sentiment analysis. Dir example, below we use the dictionnary data_dictionary_LSD2015. It provides positive and negative values. 

Frsit, we prepare the date

```{r}
boris.cp<-corpus(c(boris9mars,boris12mars,boris16mars,boris18mars,boris19mars,boris20mars,boris22mars))
summary(boris.cp)

boris.tk<-tokens(boris.cp,
                 remove_numbers = TRUE,
                 remove_punct = TRUE,
                 remove_symbols = TRUE,
                 remove_separators = TRUE)
boris.tk<-tokens_tolower(boris.tk)
boris.tk<- tokens_replace(boris.tk,pattern = hash_lemmas$token, replacement = hash_lemmas$lemma)
boris.tk<-boris.tk %>%
  tokens_remove(stopwords("english"))

```

Now we  the dunction tokens_lookup is used to match the tokens in the documents to the tokens in the dictionary and extract their corresponding value ( positive or negative)

```{r}
boris.sent<- tokens_lookup(boris.tk,dictionary = data_dictionary_LSD2015) %>% dfm() %>% tidy 
ggplot(boris.sent,aes(x=document,y=count, fill=term)) +
  geom_bar(stat="identity") + coord_flip()
```


### Using valence shifter


The sentimentr library offers some function to compute sentiments integrating valence shiter. One important apsect is that it cannot be applied to a Bag Of Word model. 
```{r}

#boris.text<-get_sentences(boris.tk$Text)
#boris.senti<-sentiment(boris.text)
#boris.senti<-as_tibble(boris.senti)

#boris.senti%>% group_by(element_id) %>%
  #ggplot(aes(x=sentence_id,y=sentiment)) +
  #geom_line() +
  #facet_wrap(~element_id)

```


## Macron

## Comparison

<!--chapter:end:Sentiment_Analysis.Rmd-->

# Similarities
```{r}
library(readr)
library(quanteda)
library(knitr)
library(kableExtra)
library(reshape2)
library(ggplot2)
```

## Boris
```{r}
## Jaccard Similarity
boris.jac <- textstat_simil(corpus_boris.tfidf, method = "jaccard", margin = "documents")
## Cosine Similarity
boris.cos <- textstat_simil(corpus_boris.tfidf, method = "cosine", margin = "documents")
## Euclidean Distance
boris.euc <- textstat_dist(corpus_boris.tfidf, method = "euclidean", margin = "documents")
## Jaccard Matrix
boris.jac.mat <- melt(as.matrix(boris.jac))
ggplot(data=boris.jac.mat, aes(x=Var1, y=Var2, fill=value)) + scale_fill_gradient2(low="yellow", high="red", mid="orange", midpoint =0.5, limit=c(0,1), name="Jaccard") + geom_tile()
## Cosine Matrix
boris.cos.mat <- melt(as.matrix(boris.cos))
ggplot(data=boris.cos.mat, aes(x=Var1, y=Var2, fill=value)) + scale_fill_gradient2(low="yellow", high="red", mid="orange", midpoint=0.5, limit=c(0,1), name="Cosine") + geom_tile()
## Euclidean Matrix
boris.euc.mat <- melt(as.matrix(boris.euc))
M <- max(boris.euc.mat$value)
boris.euc.mat$value.std <- (M-boris.euc.mat$value)/M
ggplot(data=boris.euc.mat, aes(x=Var1, y=Var2, fill=boris.euc.mat$value.std)) + scale_fill_gradient2(low="yellow", high="red", mid="orange", midpoint=0.5, limit=c(0,1),name ="Euclidean") + geom_tile()
```

```{r}
## Clustering
## Jaccard Method
boris.hc <- hclust(dist(boris.euc))
boris.hc <- hclust(dist(1 - boris.jac))
plot(boris.hc)
## Cosine Method
boris.hc <- hclust(dist(boris.euc))
boris.hc <- hclust(dist(1 - boris.cos))
plot(boris.hc)
## Dendrogram = Hierarchical Clustering
boris.clust <- cutree(boris.hc, k=3)
boris.clust
## K-means Method = Partitionning 
boris.km <- kmeans(corpus_boris.tfidf, centers=3)
boris.km$cluster
### Extracting the 10 most used words - Dendrogram
data.frame(
  clust1 = names(sort(apply(corpus_boris.tfidf[boris.clust==1,],2,sum), decreasing = TRUE)[1:10]),
  clust2 = names(sort(apply(corpus_boris.tfidf[boris.clust==2,],2,sum), decreasing = TRUE)[1:10]),
  clust3 = names(sort(apply(corpus_boris.tfidf[boris.clust==3,],2,sum), decreasing = TRUE)[1:10])
)
### Extracting the 10 most used words - K-Means
data.frame(
  clust1 = names(sort(apply(corpus_boris.tfidf[boris.km$cluster==1,],2,sum), decreasing = TRUE)[1:10]),
  clust2 = names(sort(apply(corpus_boris.tfidf[boris.km$cluster==2,],2,sum), decreasing = TRUE)[1:10]),
  clust3 = names(sort(apply(corpus_boris.tfidf[boris.km$cluster==3,],2,sum), decreasing = TRUE)[1:10])
)

```

## Macron
```{r}
## Jaccard Similarity
macron.jac <- textstat_simil(corpus_macron.tfidf, method = "jaccard", margin = "documents")
## Cosine Similarity
macron.cos <- textstat_simil(corpus_macron.tfidf, method = "cosine", margin = "documents")
## Euclidean Distance
macron.euc <- textstat_dist(corpus_macron.tfidf, method = "euclidean", margin = "documents")
## Jaccard Matrix
macron.jac.mat <- melt(as.matrix(macron.jac))
ggplot(data=macron.jac.mat, aes(x=Var1, y=Var2, fill=value)) + scale_fill_gradient2(low="yellow", high="red", mid="orange", midpoint =0.5, limit=c(0,1), name="Jaccard") + geom_tile()
## Cosine Matrix
macron.cos.mat <- melt(as.matrix(macron.cos))
ggplot(data=macron.cos.mat, aes(x=Var1, y=Var2, fill=value)) + scale_fill_gradient2(low="yellow", high="red", mid="orange", midpoint=0.5, limit=c(0,1), name="Cosine") + geom_tile()
## Euclidean Matrix
macron.euc.mat <- melt(as.matrix(macron.euc))
M <- max(macron.euc.mat$value)
macron.euc.mat$value.std <- (M-macron.euc.mat$value)/M
ggplot(data=macron.euc.mat, aes(x=Var1, y=Var2, fill=macron.euc.mat$value.std)) + scale_fill_gradient2(low="yellow", high="red", mid="orange", midpoint=0.5, limit=c(0,1),name ="Euclidean") + geom_tile()
```

## Comparison

<!--chapter:end:Similarities.Rmd-->

# Supervised learning

## Random forest

First we need to shape tje data in a dataframe. Then we call for the training. In this simple context, in order to illustrate the concepts without too long computation times, we will limit ourselves to just one training set and one test set in a 08/02 pattern. 

```{r,warning=FALSE}
# Add the speecher of each dataframe


boris_2<-as_tibble(c(boris9mars,boris12mars,boris16mars,boris18mars,boris19mars,boris20mars,boris22mars)) %>%
  rename(
  text=value)
author="Boris Johnson"
boris_supervised<- cbind(boris_2, author)

Macron_2<-as_tibble(c(macron12march,macron16march,macron13april)) %>% 
  rename(
    text = value)

author="Macron"
macron_supervised<- cbind(Macron_2, author)

combine <- rbind(boris_supervised, macron_supervised)


## Tokenization
combine_corpus<-corpus(combine)
combine_tokens<- tokens(combine_corpus, remove_numbers = TRUE, remove_punct = TRUE, remove_symbols = TRUE, remove_separators = TRUE)
##combi Lemmatization
combine_tokens <- tokens_replace(combine_tokens, pattern=hash_lemmas$token, replacement = hash_lemmas$lemma)

## Cleaning
combine_tokens = combine_tokens %>% 
  tokens_tolower() %>% 
  tokens_remove(stopwords("english"))

y<-factor(docvars(combine_tokens,"author"))

```

Now, we build the featues. To this aim, we first compute the DTM matrix.

```{r,warning=FALSE}
combine.dfm<-dfm(combine_tokens)
combine.dfm

```

```{r,warning=FALSE}
df<-data.frame(Class=y, x=combine)
index.tr<-sample(size = round(0.8*length(y)),x=c(1:length(y)),replace = FALSE)

df.tr<-df[index.tr,]
df.te<-df[-index.tr,]

library(ranger)

combine.fit<-ranger(Class~.,
                    data = df.tr)
pred.te<-predict(combine.fit,df.te)

```
In order to see the prediction quality of the model, we call the confusionMatrix function in the caret package


```{r,warning=FALSE}
library(caret)
confusionMatrix(data=pred.te$predictions,reference = df.te$Class)

```

<!--chapter:end:Supervised.Rmd-->

# Topic Modelling

In this chapter, we analzye the topics of the speechs of Boris Jonhson and Macron using LSA and LDA.

## Boris Johnson

### LSA

First, we make the DTM matrix. We are goin to use 3 dimensions.

```{r,warning=FALSE}
bmod<-textmodel_lsa(corpus_boris.dfm,nd=3)

```

To inspect the results, we can extract the matrices involved in the LSA decomposition
```{r,warning=FALSE}
head(bmod$docs)

head(bmod$features)

```
Often the first dimension in LSA is associated with the document lenght. To see if it is true, we build a scatter-plot between the document lengt and Dimension 1.

```{r,warning=FALSE}
ns<-apply(corpus_boris.dfm,1,sum) 
plot(ns~bmod$docs [,1])

```
We clearly observe that the dimension 1 is negatively correlated with the document lenght.

Now in order to make the link between the topics and the documents and the topics with term, we use biplot

```{r,warning=FALSE}
biplot(y=bmod$docs[,2:3],x=bmod$features[,2:3],
       col=c("grey","red"),
       xlab = "Dimension 2",
       ylab="Dimension 3")
```

We repeat the same analysis with TF-IDF

```{r,warning=FALSE}
bmod_2<- textmodel_lsa(corpus_boris.tfidf, nd=3)

head(bmod_2$docs)

head(bmod_2$features)
```

### LDA

We now turn to the LDA. For illustration, we will make K=5 topis. 
```{r,warning=FALSE}
K<-5
corpus_boris.dtm<- convert(corpus_boris.dfm, to="topicmodels")
lda_boris<- LDA(corpus_boris.dtm ,k=K)

```

Top terms per topic and top topic per document can be easily obtained. Belo, the six top terms and the top topic are extracted.

```{r,warning=FALSE}
terms(lda_boris,6)

topics(lda_boris,1)  ## To see the topics related to each document
```

We now build the bar plot to inspect the per-topic-per-word probabilities (beta's). We take the 10 top terms and rearrange the beta per topic according to this order. 
```{r,warning=FALSE}
beta.td.boris<-tidy(lda_boris,matrix="beta")

beta.top.term.boris<-beta.td.boris %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

beta.top.term.boris

beta.top.term.boris %>%
  mutate(term=reorder_within(term, beta, topic)) %>%
  ggplot(aes(term,beta,fill=factor(topic))) +
  facet_wrap(~topic, scales = "free") +
  coord_flip()+
  scale_x_reordered()

```

```{r,warning=FALSE}
gamma.td.boris<- tidy(lda_boris,matrix="gamma")
gamma.td.boris


gamma.td.boris %>%
  ggplot(aes(document,gamma,fill=factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~topic,scales = "free")+
  coord_flip()+
  scale_x_reordered()
```

## Macron

### LSA

```{r,warning=FALSE}
mmod<-textmodel_lsa(corpus_macron.dfm,nd=3)

```

To inspect the results, we can extract the matrices involved in the LSA decomposition
```{r,warning=FALSE}
head(mmod$docs)

head(mmod$features)

```

Often the first dimension in LSA is associated with the document lenght. To see if it is true, we build a scatter-plot between the document lengt and Dimension 1.

```{r,warning=FALSE}
ns_macron<-apply(corpus_macron.dfm,1,sum) 
plot(ns_macron~mmod$docs [,1])

```

We clearly observe that the dimension 1 is negatively correlated with the document lenght.

Now in order to make the link between the topics and the documents and the topics with term, we use biplot

```{r,warning=FALSE}
biplot(y=mmod$docs[,2:3],x=mmod$features[,2:3],
       col=c("grey","red"),
       xlab = "Dimension 2",
       ylab="Dimension 3")
```
We repeat the same analysis with TF-IDF

```{r,warning=FALSE}
mmod_2<- textmodel_lsa(corpus_macron.tfidf, nd=3)

head(mmod_2$docs)

head(mmod_2$features)
```


### LDA

We now turn to the LDA. For illustration, we will make K=5 topis. 
```{r,warning=FALSE}
K<-5
corpus_macron.dtm<- convert(corpus_macron.dfm, to="topicmodels")
lda_macron<- LDA(corpus_macron.dtm ,k=K)

lda_macron


```
Top terms per topic and top topic per document can be easily obtained. Belo, the six top terms and the top topic are extracted.

```{r,warning=FALSE}
terms(lda_macron,6)

topics(lda_macron,1)  ## To see the topics related to each document
```

We now build the bar plot to inspect the per-topic-per-word probabilities (beta's). We take the 10 top terms and rearrange the beta per topic according to this order. 
```{r,warning=FALSE}

beta.td.macron<-tidy(lda_macron,matrix="beta")

beta.top.term.macron<-beta.td.macron %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

beta.top.term.macron

beta.top.term.macron %>%
  mutate(term=reorder_within(term, beta, topic)) %>%
  ggplot(aes(term,beta,fill=factor(topic))) +
  facet_wrap(~topic, scales = "free") +
  coord_flip()+
  scale_x_reordered()

```

```{r,warning=FALSE}
gamma.td.macron<- tidy(lda_macron,matrix="gamma")
gamma.td.macron


gamma.td.macron %>%
  ggplot(aes(document,gamma,fill=factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~topic,scales = "free")+
  coord_flip()+
  scale_x_reordered()
```

## Comparison

<!--chapter:end:Topic_modelling.Rmd-->

# Word Embedding

## Boris Johnson

Here, we compute the co-occurence matrix. We use the fcm function from quanteda. We use a window lenght 5. 


```{r,warning=FALSE}
speech.coo.boris<-fcm(corpus_boris,context="window",window=5, tri=FALSE)
```

```{r,warning=FALSE}
p<-2 #word embedding dimension
speech.glove.boris<-GlobalVectors$new(rank = p,x_max = 10) #xmas is a neede technical option
speech.weC.boris<-speech.glove.boris$fit_transform(speech.coo.boris)
```
For illustration purpose, we now plot the 50 most used terms

```{r,warning=FALSE}
n.w.boris<-apply(corpus_boris.dfm,2,sum) #compute the number of times each term is used
index<-order(n.w.boris,decreasing = TRUE)[1:50]
plot(speech.weC.boris[index,],type = "n",xlab = "Dimension 1", ylab = "Dimendion 2")
text(x=speech.weC.boris[index,],labels = rownames(speech.weC.boris[index,]))
```

```{r,warning=FALSE}
speech.dtm <- corpus_boris.dfm
speech.rwmd.model.boris<-RelaxedWordMoversDistance$new(corpus_boris.dfm,speech.weC.boris)
speech.rwms.boris<-speech.rwmd.model.boris$sim2(corpus_boris.dfm)
speech.rwmd.boris<-speech.rwmd.model.boris$dist2(corpus_boris.dfm)

speech.hc.boris<-hclust(as.dist(speech.rwmd.boris))
plot(speech.hc.boris,cex=0.8)

```

We can observe that there is some coherence within the groups in terms the date of the speech. 

```{r,warning=FALSE}
speech.cl.boris<- cutree(speech.hc.boris,k=4)
corpus_boris.dfm[speech.cl.boris==1,]
```



## Macron

```{r,warning=FALSE}
speech.coo.macron<-fcm(corpus_macron,context="window",window=5, tri=FALSE)
```

```{r,warning=FALSE}
p<-2 #word embedding dimension
speech.glove.macron<-GlobalVectors$new(rank = p,x_max = 10) #xmas is a neede technical option
speech.weC.macron<-speech.glove.macron$fit_transform(speech.coo.macron)
```

For illustration purpose, we now plot the 50 most used terms

```{r,warning=FALSE}
n.w.macron<-apply(corpus_macron.dfm,2,sum) #compute the number of times each term is used
index<-order(n.w.macron,decreasing = TRUE)[1:50]
plot(speech.weC.macron[index,],type = "n",xlab = "Dimension 1", ylab = "Dimendion 2")
text(x=speech.weC.macron[index,],labels = rownames(speech.weC.macron[index,]))
```


```{r,warning=FALSE}
speech.dtm.macron <- corpus_macron.dfm
speech.rwmd.model.macron<-RelaxedWordMoversDistance$new(corpus_macron.dfm,speech.weC.macron)
speech.rwms.macron<-speech.rwmd.model.macron$sim2(corpus_macron.dfm)
speech.rwmd.macron<-speech.rwmd.model.macron$dist2(corpus_macron.dfm)

speech.hc.macron<-hclust(as.dist(speech.rwmd.macron))
plot(speech.hc.macron,cex=0.8)

```
We can observe that there is some coherence within the groups in terms the date of the speech. 

```{r,warning=FALSE}
speech.cl.macron<- cutree(speech.hc.macron,k=2)
corpus_macron.dfm[speech.cl.macron==1,]
```

## Comparison



<!--chapter:end:Word_embedding.Rmd-->

