# EDA

##Data Acquisition

To download the differents speaches we scrap the speaches on 2 differents websites.
The speaches from Macron come from the website of the Embassy of France in Washington DC (USA) and regarding Boris Johnson speaches, it comes from the official website of the governement of the United-Kingdom.

### Emmanuel Macron 

We choose the 3 first speaches from Macron about the corona virus dating from the:
  - 12 march (text1)
  - 16 march (text2)
  - 13 april (text3)

```{r include=FALSE}
packages <- c(
  "here", "readr",# for the project's organization
  "tidyverse", "lubridate", # for wrangling
  "modelr", "broom",
  "dplyr",# for modeling
  "ggrepel", "gghighlight", "patchwork", "maps", # for plotting
  "knitr", "kableExtra", "bookdown", "rmarkdown", # for the report
  "randomForest","janitor","caret","pdftools","rvest","wordcloud2","tidytext","tokenizers","quanteda","sentimentr",
  "stringr","lexicon","RColorBrewer","tm","printr","ggplot2","quanteda.textmodels","topicmodels","text2vec", "DT")

purrr::walk(packages, library, character.only = TRUE)

# automatically create a bib database for R packages
write_bib(.packages(), here::here("packages.bib"))

# Data Acquisition Macron 

macron12march <- read_html("https://franceintheus.org/spip.php?article9654") %>%
  html_nodes("div.texte") %>%
  html_text()
macron12march <- str_replace_all(macron12march,"[\r\n\t]", "")
macron12march <- substr(macron12march, 178, 20197)

macron16march <- read_html("https://franceintheus.org/spip.php?article9659#1") %>%
  html_nodes("div.texte") %>%
  html_text()
macron16march <- macron16march <- str_replace_all(macron16march,"[\r\n\t]", "")
macron16march <- substr(macron16march, 131, 15719)

macron13april <- read_html("https://franceintheus.org/spip.php?article9710") %>%
  html_nodes("div.texte") %>%
  html_text() 
macron13april <- macron13april <- str_replace_all(macron13april,"[\r\n\t]", "")
macron13april <- substr(macron13april, 117, 20000)


macron <- corpus(c(macron12march,macron16march,macron13april))
```

```{r }
summary(macron)

```
The first speaches from Macron was quite long , 162 sentences and the two next were shorter: 107 sentences. Each speech consists approximatly of an average of 3200 words.

###Boris Johnson

We choose the 7 first speaches from president Johnson about the corona virus dating from the:
  - 09 march (text1)
  - 12 march (text2)
  - 16 march (text3)
  - 18 march (text5)
  - 19 march (text6)
  - 20 march (text7)
  - 22 march (text8)

```{r include=FALSE}

# Data Acquisition Boris

boris16mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-16-march-2020") %>%
                html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>% 
                html_text()

boris12mars<- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-12-march-2020") %>%   
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris18mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-18-march-2020") %>%   
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris9mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-9-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris19mars<- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-19-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()

boris20mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-20-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()


boris22mars <- read_html("https://www.gov.uk/government/speeches/pm-statement-on-coronavirus-22-march-2020") %>% 
              html_nodes(xpath="//*[@id='content']/div[3]/div[1]/div[1]/div[2]/div") %>%
              html_text()


boris<-corpus(c(boris9mars,boris12mars,boris16mars,boris18mars,boris19mars,boris20mars,boris22mars))
```

```{r }
summary(boris) ###number of tokens and token types
```
Johnson made more speeches but shorter. His first speech was 577 words, then the following ones ranged from 729 to 1175 words.

## Tokenisation, Lemmatization & Cleaning

### Emmanuel Macron


```{r}

## Tokenization
corpus_macron <- corpus(macron)
corpus_macron <- tokens(corpus_macron, remove_numbers = TRUE, remove_punct = TRUE, remove_symbols = TRUE, remove_separators = TRUE)

## Lemmatization
corpus_macron <- tokens_replace(corpus_macron, pattern=hash_lemmas$token, replacement = hash_lemmas$lemma)

## Cleaning
corpus_macron=corpus_macron %>% 
  tokens_tolower() %>% 
  tokens_remove(stopwords("english")) 

corpus_macron

```

###Boris Johnson

```{r}

## Tokenization
corpus_boris <- corpus(boris)
corpus_boris <- tokens(corpus_boris, remove_numbers = TRUE, remove_punct = TRUE, remove_symbols = TRUE, remove_separators = TRUE)

## Lemmatization
corpus_boris <- tokens_replace(corpus_boris, pattern=hash_lemmas$token, replacement = hash_lemmas$lemma)

## Cleaning
corpus_boris = corpus_boris %>% 
  tokens_tolower() %>% 
  tokens_remove(stopwords("english")) 

corpus_boris

```

## Document-Term Matrix DTM

Now let's compute the word frequencies (TF) by documents. First, the tokens are grouped by the indicator Document, which allows to count the words by documents. The the object is ungrouped.


These frqeuencies are represented with barplots. We only keep the 15 most frequent words for redability purpose and create barplots using ggplot and geom_col. The facetwrap function split the barplots per Document.

We see that the list of 15 most frequent term are due to doc 2 ,4 and 3. 

Now we want to know which are  the most frequent term for each document

###Emmanuel Macron

```{r  include=TRUE, warning=FALSE}
## Document-Term Matrix DTM
corpus_macron.dfm <- dfm(corpus_macron)

macron_dtm <- VectorSource(corpus_macron) %>% VCorpus() %>%  DocumentTermMatrix(control=list(removePunctuation=TRUE, removeNumbers=TRUE, stopwords=TRUE))
macron_tidy <- tidy(macron_dtm)

datatable(macron_tidy, class = "cell-border stripe")

#top 15 
macron_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`)) %>%
  top_n(15)  %>%
  ggplot(aes(x=count, y=term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Macron's speeches") +
  xlab("Frequency") + ylab("Word") +
  geom_bar(stat = "identity") +
  scale_y_reordered() 

#top 15 par texte 
macron_tidy %>%
  group_by(document) %>%
  top_n(15) %>%
  ungroup() %>%
  mutate(document = factor(as.numeric(document), levels = 1:17)) %>%
  ggplot(aes(reorder_within(term, count, document), count, fill =term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Macron's speech") +
  xlab("Word") + ylab("Frequency") +
  geom_bar(stat = "identity") +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~ document, scales = "free")

#top 16 mots plus utilisés par texte
macron_count  = macron_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`))

macron_index = top_n(macron_count, 15)

macron_tidy %>% filter(term %in% macron_index$term) %>%
  ggplot(aes(x=term, y = count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```

###Boris Johnson

```{r}

## Document-Term Matrix DTM
corpus_boris.dfm <- dfm(corpus_boris)

boris_dtm <- VectorSource(corpus_boris) %>% VCorpus() %>%  DocumentTermMatrix(control=list(removePunctuation=TRUE, removeNumbers=TRUE, stopwords=TRUE))
boris_tidy <- tidy(boris_dtm)

datatable(boris_tidy, class = "cell-border stripe")


#top 15
boris_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`)) %>%
  top_n(15)  %>%
  ggplot(aes(x=count, y=term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Boris Johnson's speeches") +
  xlab("Frequency") + ylab("Word") +
  geom_bar(stat = "identity") +
  scale_y_reordered() 

#top 15 par texte
boris_tidy %>%
  group_by(document) %>%
  top_n(15) %>%
  ungroup() %>%
  mutate(document = factor(as.numeric(document), levels = 1:17)) %>%
  ggplot(aes(reorder_within(term, count, document), count, fill =term)) +
  theme(legend.position = "none") +
  ggtitle("15 most common words in Boris Johnson's speeches") +
  xlab("Word") + ylab("Frequency") +
  geom_bar(stat = "identity") +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(~ document, scales = "free")

#top 16 mots plus utilisés par texte
boris_count  = boris_tidy %>%
  group_by(term) %>%
  summarise("count"=sum(`count`))

boris_index = top_n(boris_count, 15)

boris_tidy %>% filter(term %in% boris_index$term) %>%
  ggplot(aes(x=term, y = count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```
##TF-IDF

Now we repeat the same analysis using the TF-IDF.

###Emmanuel Macron 
```{r  include=TRUE, warning=FALSE}
## TFIDF no point when just on document, maybe add when combining texts
corpus_macron.tfidf <- dfm_tfidf(corpus_macron.dfm)

#tfidf
macron_index_tfidf = tidy(corpus_macron.tfidf) %>% group_by(document) %>% top_n(1)

tidy(corpus_macron.tfidf) %>% filter(term %in% macron_index_tfidf$term) %>%
  ggplot( aes(term, count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```
###Boris Johnson


```{r}
## TFIDF no point when just on document, maybe add when combining texts
corpus_boris.tfidf <- dfm_tfidf(corpus_boris.dfm)

#tfidf
boris_index_tfidf = tidy(corpus_boris.tfidf) %>% group_by(document) %>% top_n(1)

tidy(corpus_boris.tfidf) %>% filter(term %in% boris_index_tfidf$term) %>%
  ggplot( aes(term, count)) +
  geom_col()+
  coord_flip()+
  facet_wrap(~document, ncol=2)

```
## Cloud of Words

###Emmanuel Macron 
```{r}

## Cloud of Words
textplot_wordcloud(corpus_macron.dfm, color=brewer.pal(8, "Dark2"))
textplot_wordcloud(corpus_macron.tfidf, color=brewer.pal(8, "Dark2"))

```
###Boris Johnson

```{r}

## Cloud of Words
textplot_wordcloud(corpus_boris.dfm, color=brewer.pal(8, "Dark2"))
textplot_wordcloud(corpus_boris.tfidf, color=brewer.pal(8, "Dark2"))
```

##Lexical Divesity Token Type Ratio TTR

###Emmanuel Macron 
```{r}
## Lexical Divesity Token Type Ratio TTR
N.macron <- ntoken(corpus_macron)
V.macron <- ntype(corpus_macron)
TTR.macron <- V.macron/N.macron
TTR.macron ###the text is quite poor, as TTR is of 0.4

```
###Boris Johnson

```{r}
## Lexical Divesity Token Type Ratio TTR
N.boris <- ntoken(corpus_boris)
V.boris <- ntype(corpus_boris)
TTR.boris <- V.boris/N.boris
TTR.boris ###the text is quite rich, as TTR is of 0.6

```


##Zipf's Law

Now, we illustrate the Zipf's law on the discous of Boris Jonhson. The terms are ranked by their frequency (rank=1 for the most frequent), then plotted versus its rank. This is easily obtained using quanteda.

Now on the log scale this gives a linear relation

###Emmanuel Macron 
```{r}
corpus_macron_freq <- textstat_frequency(corpus_macron.dfm)
plot(log(frequency)~log(rank), data=corpus_macron_freq, pch=20)

ggplot(corpus_macron_freq,aes(x = rank, y = frequency, label=feature)) + geom_point(size=2, alpha =1) + theme_bw() + geom_text(aes(label=feature),hjust=0, vjust=0) + xlim(0,20)


```
###Boris Johnson

```{r}

corpus_boris_freq <- textstat_frequency(corpus_boris.dfm)
plot(log(frequency)~log(rank), data=corpus_boris_freq, pch=20)

ggplot(corpus_boris_freq,aes(x = rank, y = frequency, label=feature)) + geom_point(size=2, alpha =1) + theme_bw() + geom_text(aes(label=feature),hjust=0, vjust=0) + xlim(0,20)


```





##yule's index

###Emmanuel Macron 
```{r}
textstat_lexdiv(corpus_macron.dfm, measure = "I") %>% 
  ggplot(aes(x=reorder(document,I), y=I))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("Yule's index")
```
###Boris Johnson

```{r}
textstat_lexdiv(corpus_boris.dfm, measure = "I") %>% 
  ggplot(aes(x=reorder(document,I), y=I))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("Yule's index")
```


##MATTR

###Emmanuel Macron 
```{r}
textstat_lexdiv(corpus_macron, measure = "MATTR", MATTR_window = 10)  %>%
  ggplot(aes(x=reorder(document,MATTR), y=MATTR))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("MATTR")
```
###Boris Johnson

```{r}
textstat_lexdiv(corpus_boris, measure = "MATTR", MATTR_window = 10)  %>%
  ggplot(aes(x=reorder(document,MATTR), y=MATTR))+
  geom_point()+
  coord_flip()+
  xlab("Text")+
  ylab("MATTR")

```

